---
title: "Knit engines"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knit-engines}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
code <- function(nm) paste(knitr:::knit_code$get(nm), collapse = "\n")
library(atusydown)
```

This article introduces additional knit engines.

Load `atusydown` package primarily to enable features described here.

```{.r}
library(atusydown)
```


## `glue`

The `glue` engine is useful in programatically writing texts.
As documented in `?glue::glue`,

> Expressions enclosed by braces will be evaluated as R code. Long strings are broken by line and concatenated together. Leading whitespace and blank lines from the first and last lines are automatically trimmed.

For example, let's substitute `{name}` by "Atusy".

First use `r` engine like below.

```{r atusy}
name <- "Atusy"
```

And then use `glue` engine like below.
Note that source chunk never echoes.

````{.text}
```{glue`r "}"`
`r code("glue-brace")`
```
````

```{glue glue-brace}
> **My name is {name}.**
This output is powered by glue package!
```

Nice text!
The output text is rendered as Pandoc's markdown.

Extra arguments of `glue::glue()` can be controlled by specifying `glue.args`.
A following example 
  replaces a expression enclosed by percents (`%` and `%`) 
  instead of default braces (`{` and `}`)

````{.text}
```{glue, glue.args = list(.open = "%", .close = "%")`r "}"`
`r code("glue-percent")`
```
````

```{glue glue-percent, glue.args = list(.open = "%", .close = "%")}
> **My name is %name%.**
This output is powered by glue package!
```

## `footnote` and `fn`

A `footnote` engine and its alias `fn` generates footnote whose label is
inherited from chunk label[^fn-footnote].
The `footnote` engine is powered by `glue::glue()`,
so that options are same as those of the [glue](#glue) engine.

````text
```{fn fn-footnote`r "}"`
knitr:::knit_code$get("fn-note")
```
````


```{fn fn-footnote}
This is a footnote generated by `fn` engine.
```


## `opts`

The `opts` engine returns chunk options of a current chunk.

By default, all the available options are returned.
The output of `opts` can be limited by specifying either `"diff"` or `"src"` to
a chunk option called `opts.show`.

The output of `opts` is by default sorted by names.
The sorting can be disabled by specifying `opts.sort = FALSE`.

Note that source chunk never echoes.

### Show all the chunk options (default)

````{.text}
```{opts`r "}"`
`r code("options")`
```
````

```{opts options}
The content of chunk is ignored.
```

### Show options different from `opts_chunk$get()` by `opts.show = "diff"`

Specifying `ops.show = "diff"` as a chunk option returns 
chunk options of the source chunk which have different values from
`knitr::opts_chunk$get()`.

````{.text}
```{opts opts-diff, foo = "bar", opts.show = "diff"`r "}"`

```
````

```{opts opts-diff, foo = "bar", opts.show = "diff"}

```

### Show input options in the chunk by `opts.show = "src"`

Specifying `opts.show = "src"` as a chunk option 
returns chunk options that are set in the source chunk.

````
```{opts opts-src, opts.show = "src"`r "}"`

```
````

```{opts opts-src, opts.show = "src"}

```


