---
title: "Knit hooks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knit-hooks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(atusydown)
```

## Show source chunk asis

By specifying `opts.include = TRUE`, 
the source chunk returns the chunk including its option except for `opts.include`.
Note a limitation that `collapse` is ignored.

### R chunk

````
```{r, cache = FALSE, opts.include = TRUE`r "}"`
1
```
````

gives

```{r, cache = FALSE, opts.include = TRUE}
1
```

Similary labelled chunk gives

```{r label, eval = FALSE, opts.include = TRUE}
1
```

And chunk options starting without comma gives

```{r eval = FALSE, opts.include = TRUE}
1
```

Note that chunk without codes will not be echoed, 
which is probably a default behavior of R Markdown.

### Shell chunk

```{sh, opts.include = TRUE}
echo "hello"
```

### Chunks using extra engines in atusydown

Currently, engines `glue` and `opts` do not support `opts.include`.

## Measuring elapsed time in a chunk

A chunk option with `time = TRUE` returns elapsed time.
Specify an integer to `time.digits` to round the time.
Otherwise the time rounded by `signif()`.

````
```{r, time = TRUE, time.digits = 2`r "}"`
`r knitr:::knit_code$get("time")`
```
````

```{r time, time = TRUE, time.digits = 2, echo = FALSE}
Sys.sleep(time = 1e-2)
```


